---
title: "AS03_join_edu_data"
author: "Jilung Hsieh"
date: "9/25/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: no
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readr)
options(stringsAsFactors = F)
```

# Q1 Joining educational data
- Reading educational data from the following csv file.

## Reading education data
```{r}
raw2 <- read_csv("data/opendata107Y020.csv") %>%
    slice(-1) %>%
    glimpse()
```


## Town level educational data 
- Original data is village-level data
- Following In-Class tutorial, using `group_by()` to create town-level statistical data.
```{r}
tidydata2 <- raw2 %>%
  gather("key", "value", 6:ncol(.)) %>%
  mutate(key = str_replace(key, "edu_", "")) %>%
  mutate(key = str_replace(key, "juniorcollege_2ys", "juniorcollege2ys")) %>%
  mutate(key = str_replace(key, "juniorcollege_5ys_final2y", "juniorcollege5ysfinal2y")) %>%
  mutate(key = str_replace(key, "juniorcollege_5ys_first3y", "juniorcollege5ysfirst3y")) %>%
  mutate(key = str_replace(key, "illiterate_", "illiterate_NA_")) %>%
  mutate(key = str_replace(key, "selftaughtl_", "selftaughtl_NA_")) %>%
  mutate(key = str_replace(key, "juniorcollege_5ys_first3y_ungraduated", "juniorcollege5ysfirst3y_ungraduated")) %>%
  separate(key, c("education", "grad_status", "gender"))
```

```{r}
town_edu <- tidydata2 %>%
  select(-village) %>%
  mutate(value = as.numeric(value), edu_age_15up_total = as.numeric(edu_age_15up_total)) %>%
  group_by(site_id) %>%
  summarize(
    male_total = sum(value[gender=="m"]),
    female_total = sum(value[gender=="f"]),
    edu_above_junior = sum(value[education=="university" | education=="master" | education=="doctor"])
  ) %>%
  arrange(edu_above_junior)
```


## Add code chunks as you need here.

## Loading town-level age, marriage, and referendum data
- Loading town-level data created in class

```{r}
town_stat <- read_rds("./data/hw3/town_stat.rds")
town_ref10 <- read_rds("./data/hw3/town_ref10.rds")
```



## Joining data together
- Joining all town-leave data together (Including new educational dada, and age, marriage, referendum data introduced in class)
```{r}
town_edu_ref10_stat <- town_edu %>%
  right_join(town_stat, by="site_id") %>%
  right_join(town_ref10, by=c("site_id"="townfull")) 
```

## **Q1 Ans: Joined data dimension**
- using `dim()` to display data dimension (should be 368). TAs will score Q1 according to the outcome.
```{r}
dim(town_edu_ref10_stat)
```


## **Q1 Ans: glimpse()**
- Using `glimpse()` to print out data you join below. TAs will score Q1 according to the `glimpse()` outcome.
```{r}
glimpse(town_edu_ref10_stat)
```

# Q2 Open Question - Joining one more dimension
- TASK: Collecting one more dimension from open data for town level and join it with the eucation, married, age, and referendum data.

## Read the file
```{r}
folder <- './data/hw3/'
file <- list.files(folder, pattern="*.csv")
raw <- lapply(paste0(folder, file), read_csv, skip=1)
data <- bind_rows(raw)
data <- na.omit(data)
```

## Display the data dimension of the file
```{r}
dim(data)
```

## aggregate and make it into town level
```{r}
names(data) <- c("type", "y", "place")
crime_data <- data %>%
  select(-2) %>%
  group_by(place) %>%
  summarize(
    crime_total = n()
  )
```


## **Q2 Ans: Answer following questions**
- Data source link (the page you download the data): 
- Describe the data source in your words: 

# https://data.moi.gov.tw/MoiOD/Data/DataDetail.aspx?oid=AC4C5CF9-682A-450A-8405-45706B8C9588
- 提供毒品、強盜、搶奪、住宅盜竊、汽車竊盜、機車竊盜、強制性交等8案類犯罪發生資料 (本資料為每季初步統計，僅供參考，正確統計數字仍以本署年度刑案統計資料為準。)(自107年10月起提供組織犯罪案類資料。) 資料年度為107年度整年

## **Q2 Ans: Dim() of joined data frame**

```{r}
town_edu_ref10_stat_crime <- town_edu_ref10_stat %>%
  left_join(crime_data, by=c("site_id"= "place")) 
dim(town_edu_ref10_stat_crime)
```


## **Q2 Ans: glimpse() of joined data frame**
```{r}
glimpse(town_edu_ref10_stat_crime) 
```

# Q3 Open question - Linear regression
 - Now, you have age, marriage, and education as indenpendent variables and referendum 10th agreement as the dependent variable.
 - Go online and search how to run regression with R
 - Report the regression result 

## **Q3 Ans**
```{r}
linearMod <- lm(crime_total ~ edu_above_junior, data=town_edu_ref10_stat_crime)  
# build linear regression model on full data

# code for print out regression result 
linearMod
plot(x = town_edu_ref10_stat_crime$edu_above_junior, y = town_edu_ref10_stat_crime$crime_total, xlab = "edu_above_junior", ylab = "crime_total", main = "Education level and crime rate")
abline(linearMod)
```



# Q4 Challenge: The median of grouped data
- Calculating age median of grouped data
- Reference: https://www.themathdoctors.org/finding-the-median-of-grouped-data/
- Solve it wit dplyr pkgs
- If you can't answer the question correctly, keep your code (even wrong) to get partial scores.

## **Q4 Ans: glimpse()**
```{r}

#glimpse(YOUR_DATA_FRAME_NAME)
```

